Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-03-20 2024pipit/section/01-Introduction.tex
contributions fix

\begin{itemize}
  \item we motivate the need to combine manual and automated proofs of reactive systems with a strong specification language (\autoref{s:motivation});
  \item we introduce Pipit, a minimal reactive language that supports rely-guarantee contracts and properties; crucially, proof obligations are annotated with a status --- \emph{valid} or \emph{deferred} --- allowing proofs to be delayed until more is known of the program context (\autoref{s:core});
  \item we describe a \emph{checked semantics} for Pipit, which is parameterised by the property status; after checking deferred properties, programs can be \emph{blessed}, and their properties lifted to valid status (\autoref{s:core:checked});
  \item we describe an encoding of transition systems that can express under-specified rely-guarantee contracts as functions rather than relations; composing functions results in simpler transition systems (\autoref{s:transition});
  \item we identify the invariants and lemmas required to prove that the abstract transition system is an abstraction of the original semantics (\autoref{s:core:causality}, \autoref{s:transition:proof});
  \item similarly, we offer a mechanised proof that the executable transition system preserves the original semantics (\autoref{s:extraction});
  \item finally, we evaluate Pipit by implementing a time-triggered CAN bus driver, which we have partially verified (\autoref{s:evaluation}).
\end{itemize}

>>>>

\begin{itemize}
  \item we motivate the need to combine manual and automated proofs of reactive systems with a strong specification language (\autoref{s:motivation});
  \item we introduce Pipit, a minimal reactive language that supports rely-guarantee contracts and properties; crucially, proof obligations are annotated with a status --- \emph{valid} or \emph{deferred} --- allowing proofs to be delayed until more is known of the program context (\autoref{s:core});
  \item we describe a \emph{checked semantics} for Pipit, which is parameterised by the property status; after checking deferred properties, programs can be \emph{blessed}, and their properties lifted to valid status (\autoref{s:core:checked});
  \item we describe an encoding of transition systems that can express under-specified rely-guarantee contracts as functions rather than relations; composing functions results in simpler transition systems (\autoref{s:transition});
  \item we identify the invariants and lemmas required to prove that the abstract transition system is an abstraction of the original semantics (\autoref{s:core:causality}, \autoref{s:transition:proof});
  \item similarly, we offer a mechanised proof that the executable transition system preserves the original semantics (\autoref{s:extraction});
  \item finally, we evaluate Pipit by implementing the high-level logic of a time-triggered Controller Area Network (CAN) bus driver and verifying an abstract model of a key component (\autoref{s:evaluation}).
\end{itemize}
